Probabilistic Forecasts in Hierarchical~Time~Series

### 2018-04-18 ProbabilisticCoherence.tex
Ellitpical theorem statement - proof to follow

\documentclass[a4paper, 11pt]{article}
\usepackage{monashwp}
\usepackage{amssymb, qtree, bm, multirow, textcmds, siunitx}
\usepackage{mathrsfs, float, booktabs,todonotes}
\usepackage[bb=boondox]{mathalfa}
\usepackage{tikz}
\usetikzlibrary{arrows,positioning,shapes,fit,calc}
\usepackage{amsfonts}
\hypersetup{citecolor=blue,linkcolor=blue,urlcolor=blue}
\DeclareNameAlias{sortname}{last-first}
\DeclareMathOperator*{\argmin}{arg\,min}
\newcolumntype{L}{>{$}l<{$}} % math-mode version of "l" column type
\def\mathbi#1{\textit{ #1}}
\def\mathB#1{\textbf{ #1}}
\def\E{\text{E}}
\mathtoolsset{showonlyrefs=true}

@@

\newtheorem{definition}{Definition}[section]

@@

%Equation \eqref{ex:2.1} implies $\tilde{\bm{b}}_{t+h} \sim \mathcal{N}(\bm{P}\bm{\hat{\mu}}_{t+h}, \bm{P}\hat{\bm{\Sigma}}_{t+h}\bm{P}')$, where $\bm{P} = (\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot$. Then from \eqref{4.7} it follows that
%\begin{equation}\label{eq:gaussianreconciled}
%\tilde{\bm{f}}(\tilde{\bm{y}}_{t+h})=\tilde{\bm{f}}(\bm{S}\tilde{\bm{b}}_{t+h}).
%\end{equation}
Which implies that the reconciled probabilistic forecast for the bottom level series is $\tilde{\bm{b}}_{t+h} \sim \mathcal{N}(\bm{P}\bm{\hat{\mu}}_{t+h}, \bm{P}\hat{\bm{\Sigma}}_{t+h}\bm{P}')$.  The reconciled probabilistic forecasts for the whole hierarchy follow a degenerate Gaussian distribution with mean  $\bm{SG}\bm{\hat{\mu}}$ and rank deficient covariance matrix $\bm{SP}\hat{\bm{\Sigma}}_{t+h}\bm{P}'\bm{S}'$.

>>>>

\documentclass[a4paper, 11pt]{article}
\usepackage{monashwp}
\usepackage{amssymb, qtree, bm, multirow, textcmds, siunitx}
\usepackage{mathrsfs, float, booktabs,todonotes,amsthm}
\usepackage[bb=boondox]{mathalfa}
\usepackage{tikz}
\usetikzlibrary{arrows,positioning,shapes,fit,calc}
\usepackage{amsfonts}
\hypersetup{citecolor=blue,linkcolor=blue,urlcolor=blue}
\DeclareNameAlias{sortname}{last-first}
\DeclareMathOperator*{\argmin}{arg\,min}
\newcolumntype{L}{>{$}l<{$}} % math-mode version of "l" column type
\def\mathbi#1{\textit{ #1}}
\def\mathB#1{\textbf{ #1}}
\def\E{\text{E}}
\mathtoolsset{showonlyrefs=true}

@@

\theoremstyle{theo}
\newtheorem{theo}{Theorem}[section]

\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]

@@

%Equation \eqref{ex:2.1} implies $\tilde{\bm{b}}_{t+h} \sim \mathcal{N}(\bm{P}\bm{\hat{\mu}}_{t+h}, \bm{P}\hat{\bm{\Sigma}}_{t+h}\bm{P}')$, where $\bm{P} = (\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot$. Then from \eqref{4.7} it follows that
%\begin{equation}\label{eq:gaussianreconciled}
%\tilde{\bm{f}}(\tilde{\bm{y}}_{t+h})=\tilde{\bm{f}}(\bm{S}\tilde{\bm{b}}_{t+h}).
%\end{equation}
Which implies that the reconciled probabilistic forecast for the bottom level series is $\tilde{\bm{b}}_{t+h} \sim \mathcal{N}(\bm{P}\bm{\hat{\mu}}_{t+h}, \bm{P}\hat{\bm{\Sigma}}_{t+h}\bm{P}')$.  The reconciled probabilistic forecasts for the whole hierarchy follow a degenerate Gaussian distribution with mean  $\bm{SG}\bm{\hat{\mu}}$ and rank deficient covariance matrix $\bm{SP}\hat{\bm{\Sigma}}_{t+h}\bm{P}'\bm{S}'$.
\subsection{Elliptical Distributions}
We now show that if the mapping $g(.)$ in definition $\ref{def:reconpoint}$ is extended to allow for a translation by ${\bm d}$, i.e. $g({\bm y})={\bm G}{\bm y}+{\bm d}$, then the true predictive distribution can be recovered for elliptical distributions.
\begin{theo}[Reconciliation for Elliptical Distributions]
	Let an unreconciled probabilistic forecast come from the elliptical class with location parameter $\hat{\bm \mu}$ and scale matrix $\hat{\bm \Sigma}$.  Let the true predictive distribution of ${\bm y}_{t+h|t}$ also belong to the elliptical class with location parameter ${\bm \mu}$ and scale matrix ${\bm \Sigma}$.  Then the affine reconciliation mapping $g({\bm y})={\bm G}{\bm y}+{\bm d}$ with $\bm{G}={\bm\Omega}^{1/2}{\bm\Sigma}^{-1/2}$ where $\bm\Omega$ is the bottom level true variance covariance matrix and ${\bm d}={\bm SG}\left({\bm \mu}-\hat{\bm \mu}\right)$ recovers the true predictive density. 
\end{theo}
\begin{proof}
  It follows from the closure of elliptical densities under affine transformations and marginalisation.  NEED TO WRITE UP!
\end{proof}
